\textbf{Computation and Neural Manifolds}

### 2025-04-24 Neural-Manifolds/neural-manifolds_v0.tex
one potato at the time
crazy ideas

% TODO - add graph from the Sohn et al 2019

@@

\section{How it is being computed?}
\begin{frame}
\frametitle{\textbf{How it is being computed?} }
Manifolds are also evidence for how something is being computed.

@@

the second computation was a porjection from the manifold onto what they called an encoding dimension.

@@

>>>>

% TODO - add graph from the Sohn et al 2019
% Need to add the arrows to the Graph

@@

\section{How it is being computed?}
\begin{frame}
\frametitle{\textbf{How it is being computed?} }

% Might need to break the information on more slides

Manifolds are also evidence for how something is being computed.

@@

\centering
\begin{minipage}{1\textwidth}
    \centering
    \includegraphics[width=0.2\textwidth]{images/Sohn_et_al-2019_05.PNG} % Replace with your image file
    \captionof{figure}{temporal interval estimation}
\end{minipage}

the second computation was a projection from the manifold onto what they called an encoding dimension.

@@

% #########################################################################################
% #########################################################################################
% Slide XX - Crazy Ideas
% #########################################################################################
% #########################################################################################

\section{Crazy Ideas}
\begin{frame}
\frametitle{Crazy Ideas}

Take the idea of the Feynman's path integral as inspiration.

The brain computes by creating and manipulating representations of reality, effectively building models that allow for prediction and manipulation of the world. Computing is not just about processing data (the change of states), but about creating and using representations that have meaning.

These representations can be expressed as manifolds.

As it tranverses the manifold we observe a change of phase which can be descirbed in information geometry and the former statistical mechanics as related to likelihood. (attention to the Hodge operator). If we consider that there are many paths to start at a simplicial representation and to achive a simplicial go and the path is the computation. We can say that all computations that are within the path of least ACTION constructively interferes and all other paths destructively interferes.

Need to extend the Approximate Bayesian Computation (ABC)

% the Hodge star operator can be used to define duality in the space of probability distributions. 
% The Hodge operator can be used to relate likelihood functions (which express the probability of observing data given a model) to the geometry of the model space.
% ℏ (pronounced "h-bar") represents the reduced Planck constant
